### 2018-01-10 documents/PRACoverLetter/PRACoverLetter.tex
Elie's modifications to the cover letter

We hereby submit our manuscript, "Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure".

% Paragraph 1: Why look for non-classical, quantum correlations?

A necessary ingredient of any manifestly quantum technology is the exploitation of some quantum phenomena which fails to be emulated by classical resources. Inherently, the advantage of quantum resources is their ability to violate correlation constraints satisfied by all classical correlations. A primal objective of quantum information theory and quantum foundations is to discover new and practical situations wherein quantum theory offers an advantage and to quantify that advantage via inequality constraints. Developing tools which solve this foundational problem in turn enhance out ability to assess the limitations and capabilities of quantum computational algorithms and quantum communication protocols.

% Paragraph 2: The Triangle Structure and the long-standing unsolved problem.

Arguably the most prominent scenario in which such inequality constraints have been derived is the Bell structure, for which the inequalities are known as Bell inequalities. The Bell structure consists of two distant parties each making measurements on their respective portions of a shared bipartite state. The focus of the present submission is to progress our understanding of analogous constraints for a superficially simple structure called the Triangle structure wherein three parties arrange themselves in a triangle and each make measurements on respective portions of three bipartite states. Despite numerous attempts by other authors, finding inequalities constraining classical correlations for the Triangle structure which admit violations by quantum resources as heretofore remained a long-standing open problem.

% Paragraph 3: Achievements of this submission.

This submission provides a resolution to this problem, by reporting the derivation of several polynomial inequalities for the Triangle structure which, importantly, are violated by quantum resources. Three qualitatively distinct inequalities are reported in the document for discussion. These inequalities constitute the first verification of genuine non-classical behaviour in the Triangle structure, promoting its exploitation for quantum technologies. Moreover, we demonstrate that these inequalities are suitable measures of non-classicality for experimental correlations as they are robust to a suitable degree of noise.

% Paragraph 4: Future outlook.

Perhaps of chief importance, new methods and tools where developed in pursuit of obtaining these results. In particular, these inequalities were derived using a novel technique for solving general causal inference problems known as the Inflation Technique. This submission demonstrates that the Inflation Technique has leading utility for studying and identifying genuine quantum correlations in more involved scenarios and consequently, in the discovery of new quantum resources.

In consideration of the aforementioned achievements and insights, we are confident this submission meets PRA's standards.

Sincerely,

Thomas C. Fraser and Elie Wolfe
}
\end{letter}

>>>>

We hereby submit our manuscript, “Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure”.

A necessary ingredient of any manifestly quantum technology is the capitalization of some quantum phenomenon which cannot be emulated by classical resources. Consequently, a foundational objective of quantum information theory is the characterization of situations wherein quantum resources offer unique advantages. Our manuscript concerns the exceptionally paradigmatic ability of quantum theory to violate certain constraints which are satisfied by all classical correlations.

The dual practices of deriving classically-inviolable inequality constraints, and quantifying their violation by quantum resources, have proven enormously effective in the development of quantum computational algorithms and quantum communication protocols. The first situation studied in this manner consisted of two distant parties each making measurements on their respective portions of a shared bipartite state; the pertinent inequalities there being the famous Bell inequalities. This specific type of cataloging of quantumness – of which the violation of Bell inequalities is emblematic – has since been extended to other situations involving multiple parties, sharing multiple states in a variety of configurations.

However, a particular configuration of state-sharing, technically-termed “cyclic”, has proven heretofore intractable. The simplest cyclic situation is the “Triangle” structure, wherein three parties each make measurements on respective portions of three bipartite states. Although a variety of classically-inviolable inequalities for the Triangle structure have been derived in the last few years, none of those initial inequalities could be shown to admit violation by quantum resources. Identifying a quantumly-violable yet classically-inviolable inequality for the Triangle structure has persisted as a longstanding and vexing open problem, despite numerous attempts by other authors.

Our submission provides resolution to this problem. We derive several classically-inviolable inequalities for the Triangle structure which are demonstrably violated by quantum resources. We discuss three qualitatively-distinct inequalities in particular. A consequence of our derivation is that – for the first time – it is now possible to robustly verify manifestly quantum behaviors in the Triangle structure. As such, our submission opens the door for the Triangle structure to be capitalized in quantum technologies.

Moreover, the pursuit of our results also sheds informative light on lesser-known mathematical methods.  For instance, in deriving our inequalities we utilized the so-called “Inflation Technique” for solving general causal inference problems. The Inflation Technique was developed for the explicit purpose of identifying manifestly quantum behaviors; our manuscript is the first practical validation that the technique is indeed capable of doing so.

In consideration of the aforementioned achievements and insights contributed by our manuscript, we are confident that this submission meets PRA’s high standards of substantiveness and significance. In preparing this submission for PRA, we have taken care to write the text in a deliberate style that is both clear and comprehensive.

Sincerely,
Thomas C. Fraser and Elie Wolfe
}
\end{letter}
